Path Analysis Data Development - Chapter 2

### 2016-02-25 sem-data-development.Rmd
Add code for calculating lagged rainfall variables.

# Untagged dbh data
untagged_dbh_2005 <- read.csv("analysis/data/untagged_dbh2005_summary.csv")
untagged_dbh_2014 <- read.csv("analysis/data/untagged_dbh2014_summary.csv")
canopy_cover <- read.csv("analysis/data/plot_canopy_cover_dens.csv")
```
```{r load physical data, echo=FALSE, message=F}
# Physical environment: topography
library(rgdal); library(plyr); library(dplyr)
plots_shp <- readOGR("analysis/data/plot_gis/", "soco_plots_metric")
plots_env <- plots_shp@data
summary(plots_env)
plots_env <- select(plots_env, -cat, -X, -Y)

@@

pairs(na.omit(select(oak_sod, c(3:4,7:8,9:10), H.2005, H.2014)),
      lower.panel = panel.cor, diag.panel = panel.hist, 
      main = "Oak-SOD Infection & Diversity Data")
```

@@

### Update path analysis data
Updating the path analysis data with the temperature during wet days variables.
```{r update data}
# load("pathmodel_data_20160112.RData")
wet_hrs <- read.csv("analysis/data/wet-days-temperature-variables.csv")
save.image("~/GitHub/superspreaders/pathmodel_data.RData")
```

>>>>

# Canopy cover from densiometer readings
canopy_cover <- read.csv("analysis/data/plot_canopy_cover_dens.csv")
```
```{r load physical data, echo=FALSE, message=F}
# Physical environment: topography
library(rgdal); library(plyr); library(dplyr)
plots_shp <- readOGR("analysis/data/plot_gis/", "soco_plots_metric")
plots_env <- plots_shp@data
summary(plots_env)
plots_env <- select(plots_env, -cat, -X, -Y)

@@

filter(oak_sod, is.na(elevation))
oak_sod <- filter(oak_sod, plotid != "ponti01", plotid != "sweet01")
filter(oak_sod, is.na(hrs_14_20_rs))
oak_sod <- filter(oak_sod, plotid != "bush01")
filter(oak_sod, is.na(H.2005))$plotid
oak_sod <- filter(oak_sod, plotid != "mcneil03", plotid != "sumtv02",
                  plotid != "votru01")
filter(oak_sod, is.na(hrs_abv25rs))# I believe these locations actually did not have any temperatures above 25 C during the rainy season
oak_sod$hrs_abv25rs[is.na(oak_sod$hrs_abv25rs)] <- 0

length(unique(oak_sod$plotid))# 164 plots remaining

pairs(na.omit(select(oak_sod, c(3,4,7:10), H.2005, H.2014)),
      lower.panel = panel.cor, diag.panel = panel.hist, 
      main = "Oak-SOD Infection & Diversity Data")
```

I'm going to add some lag variables, e.g. average rainfall for time t + t-1 or t-1 + t-2.
```{r create lag variables}
library(tidyr)
summary(rain_total)
unique(rain_total$sample_year)
rain_lag <- as.tbl(select(rain_total, plotid, sample_year, rain_tot_v))
rain_lag1 <- as.tbl(select(rain_total, plotid, sample_year))
rain_lag1 <- rain_lag1 %>% 
      mutate(sample_year_minus1 = sample_year - 1, 
             sample_year_minus2 = sample_year - 2,
             sample_year_minus3 = sample_year - 3) 
rain_lag1 <- left_join(rain_lag1, rain_lag,
                by = c("plotid", "sample_year_minus1"="sample_year")) %>%
      rename(rain_tot_t_minus1 = rain_tot_v)
rain_lag1 <- left_join(rain_lag1, rain_lag,
                by = c("plotid", "sample_year_minus2"="sample_year")) %>%
      rename(rain_tot_t_minus2 = rain_tot_v)
rain_lag1 <- left_join(rain_lag1, rain_lag,
                by = c("plotid", "sample_year_minus3"="sample_year")) %>%
      rename(rain_tot_t_minus3 = rain_tot_v)
rain_lag1 <- left_join(rain_lag1, rain_lag,
                by = c("plotid", "sample_year"="sample_year"))
rain_lag1 <- select(rain_lag1, plotid, sample_year, starts_with("rain"))

rain_lag1 <- rain_lag1 %>% 
      mutate(avg_rain_t_minus1 = 
                   rowMeans(cbind(rain_tot_v, rain_tot_t_minus1)),
             avg_rain_t_minus2 =
                   rowMeans(cbind(rain_tot_v, rain_tot_t_minus1, rain_tot_t_minus2)),
             avg_rain_t1t2 = rowMeans(cbind(rain_tot_t_minus1, rain_tot_t_minus2)))
summary(rain_lag1)
```

@@

### Update path analysis data
Updating the path analysis data with the temperature during wet days variables.
```{r update data}
# load("pathmodel_data_20160112.RData")
# Add untagged dbh data
untagged_stems <- read.csv("analysis/data/untagged_stems_corrected.csv")
untagged_dbh_2005 <- read.csv("analysis/data/untagged_dbh2005_summary.csv")
untagged_dbh_2014 <- read.csv("analysis/data/untagged_dbh2014_summary.csv")

wet_hrs <- read.csv("analysis/data/wet-days-temperature-variables.csv")
save.image("~/GitHub/superspreaders/pathmodel_data.RData")
```
